---
title: "Github page"
output:
  html_document:
    theme: lumen
    highlight: tango
    toc: yes
    toc_position: right
    toc_float: yes
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(lingtypology)
```

### Typology of Iconicity Patterns in Sign Languages

This page represents sign languages' preferences for iconicity patterns and iconicity bases in respect to different iconic signs.

Here is a link to download our dataset: [.csv](https://raw.githubusercontent.com/Pandaklez/Iconicity-in-Sign-Languages/master/annotated_data_new.csv)

### window

```{r}
df <- read.csv("window.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bicycle

```{r}
df <- read.csv("bicycle.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### truck

```{r}
df <- read.csv("truck.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### boat

```{r}
df <- read.csv("boat.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### tie

```{r}
df <- read.csv("tie.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### hat

```{r}
df <- read.csv("hat.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### socks

```{r}
df <- read.csv("socks.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### elephant

```{r}
df <- read.csv("elephant.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cat

```{r}
df <- read.csv("cat.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### giraffe

```{r}
df <- read.csv("giraffe.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### pear

```{r}
df <- read.csv("pear.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cucumber

```{r}
df <- read.csv("cucumber.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sausage

```{r}
df <- read.csv("sausage.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sun

```{r}
df <- read.csv("sun.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sky

```{r}
df <- read.csv("sky.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### tree

```{r}
df <- read.csv("tree.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### hammer

```{r}
df <- read.csv("hammer.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### shovel

```{r}
df <- read.csv("shovel.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### house

```{r}
df <- read.csv("house.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### wardrobe

```{r}
df <- read.csv("wardrobe.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### armchair

```{r}
df <- read.csv("armchair.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### lamp

```{r}
df <- read.csv("lamp.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### chair

```{r}
df <- read.csv("chair.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### moon

```{r}
df <- read.csv("moon.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### flower

```{r}
df <- read.csv("flower.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sand

```{r}
df <- read.csv("sand.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sea

```{r}
df <- read.csv("sea.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### car

```{r}
df <- read.csv("car.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### plane

```{r}
df <- read.csv("plane.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### train

```{r}
df <- read.csv("train.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bus

```{r}
df <- read.csv("bus.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### underground

```{r}
mdf <- read.csv("underground.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### tram

```{r}
df <- read.csv("tram.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### motorbike

```{r}
df <- read.csv("motorbike.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### helicopter

```{r}
df <- read.csv("helicopter.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### taxi

```{r}
df <- read.csv("taxi.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### ship

```{r}
df <- read.csv("ship.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### balloon

```{r}
df <- read.csv("balloon.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### mountain

```{r}
df <- read.csv("mountain.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### island

```{r}
df <- read.csv("island.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### river

```{r}
df <- read.csv("river.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### star

```{r}
df <- read.csv("star.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### lightning

```{r}
df <- read.csv("lightning.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### rainbow

```{r}
df <- read.csv("rainbow.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cloud

```{r}
df <- read.csv("cloud.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### forest

```{r}
df <- read.csv("forest.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### lake

```{r}
df <- read.csv("lake.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### fire

```{r}
df <- read.csv("fire.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cave

```{r}
df <- read.csv("cave.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### desert

```{r}
df <- read.csv("desert.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### wave

```{r}
df <- read.csv("wave.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### fork

```{r}
df <- read.csv("fork.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### spoon

```{r}
df <- read.csv("spoon.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### knife

```{r}
df <- read.csv("knife.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### tooth_brush

```{r}
df <- read.csv("tooth_brush.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### comb

```{r}
df <- read.csv("comb.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bear

```{r}
df <- read.csv("bear.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### dog

```{r}
df <- read.csv("dog.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### lion

```{r}
df <- read.csv("lion.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bird

```{r}
df <- read.csv("bird.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cow

```{r}
df <- read.csv("cow.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### frog

```{r}
df <- read.csv("frog.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### turtle

```{r}
df <- read.csv("turtle.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### meat

```{r}
df <- read.csv("meat.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### banana

```{r}
df <- read.csv("banana.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cake

```{r}
df <- read.csv("cake.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bread

```{r}
df <- read.csv("bread.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### pineapple

```{r}
df <- read.csv("pineapple.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### lemon

```{r}
df <- read.csv("lemon.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### carrot

```{r}
df <- read.csv("carrot.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### skirt

```{r}
df <- read.csv("skirt.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### sweater

```{r}
df <- read.csv("sweater.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bracelet

```{r}
df <- read.csv("bracelet.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### scarf

```{r}
df <- read.csv("scarf.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### T-shirt

```{r}
df <- read.csv("T-shirt.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### trousers

```{r}
df <- read.csv("trousers.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### blouse

```{r}
df <- read.csv("blouse.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### cup

```{r}
df <- read.csv("cup.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### kettle

```{r}
df <- read.csv("kettle.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### key

```{r}
df <- read.csv("key.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### door

```{r}
df <- read.csv("door.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### room

```{r}
df <- read.csv("room.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### bed

```{r}
df <- read.csv("bed.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### table

```{r}
df <- read.csv("table.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### fox

```{r}
df <- read.csv("fox.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### mouse

```{r}
df <- read.csv("mouse.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### spider

```{r}
df <- read.csv("spider.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```

### duck

```{r}
df <- read.csv("duck.csv")
df$urls <- sapply(df$urls, function(x){
  paste(c("<video width='250' height='200' controls> <source src='",
          as.character(x),
          "' type='video/mp4'></video>"), sep = "", collapse = "")})
set.seed(4)
map.feature(languages = df$languages,
            features = df$pattern,
            stroke.features = df$base,
            popup = df$urls,
            title = df$word[1])
```
